### 2015-07-12 narrative/intro.tex
refer to our system as SIRUS.

%%% Manish: I am not sure I fully understand the first part of the paragraph
%%% below.
The proposed work explores how application-specific information about the
importance of data will be used in conjunction with system and
resource-specific information to optimize the scientists' experience in
interacting with, and extracting knowledge and insight from their data.
%
%The overarching idea of this proposal is that data from applications can be characterized by different
%%levels of importance and different 
%levels of importance over time, which then can be used to guide the
% analysis and visualization later to access the most important data and
% deliver some level of knowledge without waiting for access to the whole
% original dataset. Information about the importance of the data at the
% application level, information about resource status and performance of
% the multi-level storage system, and flexible data reorganization and
% reduction operations at all levels can be utilized to provide a quality of
% service and allow users to gain insight in a timely manner.
The project combines knowledge and expertise 
from a wide range of sources including many leadership class applications using the Adaptable Input/Output System (ADIOS) framework,
the Sandia National Laboratory (SNL) Lightweight File Systems (LWFS) project and storage system knowledge, the metadata
management and storage systems knowledge at UCSC, and the middleware expertise
at Rutgers. We will integrate this diverse expertise to investigate how to create
a data, workflow, and application aware storage and I/O system.
%This project brings together a team with strong expertise in I/O middleware (ORNL, Rutgers),
%file system (SNL, UCSC) and storage (UCSC), and connects and
%coordinates these key storage components in a seamless fashion.
%
%\section{Scalable Storage Software Infrastructure}
%Our focus in this proposal is in Theme 2: {\em Scalable Storage Software Infrastructure} 
%We will focus on a state of the art SSIO solution to solve problems which researchers are 
%beginning to face and will make science on exascale systems
%problematic without new insights and solutions.
Our proposal will be responsive to Theme 2: {\em Scalable Storage Software Infrastructure} of the call, as summarized in Table~\ref{tab:call}.

>>>>

%%% Manish: I am not sure I fully understand the first part of the paragraph
%%% below.
The proposed work explores how application-specific information about the
importance of data will be used in conjunction with system and
resource-specific information to optimize the scientists' experience in
interacting with, and extracting knowledge and insight from their data.
%
%The overarching idea of this proposal is that data from applications can be characterized by different
%%levels of importance and different 
%levels of importance over time, which then can be used to guide the
% analysis and visualization later to access the most important data and
% deliver some level of knowledge without waiting for access to the whole
% original dataset. Information about the importance of the data at the
% application level, information about resource status and performance of
% the multi-level storage system, and flexible data reorganization and
% reduction operations at all levels can be utilized to provide a quality of
% service and allow users to gain insight in a timely manner.
The project combines knowledge and expertise 
from a wide range of sources including many leadership class applications using the Adaptable Input/Output System (ADIOS) framework,
the Sandia National Laboratory (SNL) Lightweight File Systems (LWFS) project and storage system knowledge, the metadata
management and storage systems knowledge at UCSC, and the middleware expertise
at Rutgers. We will integrate this diverse expertise to investigate how to create
a data, workflow, and application aware storage and I/O system, which we refer to as
{\bf SIRUS}.
%This project brings together a team with strong expertise in I/O middleware (ORNL, Rutgers),
%file system (SNL, UCSC) and storage (UCSC), and connects and
%coordinates these key storage components in a seamless fashion.
%
%\section{Scalable Storage Software Infrastructure}
%Our focus in this proposal is in Theme 2: {\em Scalable Storage Software Infrastructure} 
%We will focus on a state of the art SSIO solution to solve problems which researchers are 
%beginning to face and will make science on exascale systems
%problematic without new insights and solutions.
Our proposal will be responsive to Theme 2: {\em Scalable Storage Software Infrastructure} of the call, as summarized in Table~\ref{tab:call}.
